Are We Reusing Outdated and License-violating Code \newline from Stack Overflow?

### 2017-01-24 cloneoverflow-latex/cloneoverflow.tex
Revamped Table 4.

\documentclass{sig-alternate-05-2015}
\usepackage[utf8]{inputenc}
\usepackage[italian]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{cleveref}
\usepackage{subcaption}

@@

\begin{table}
	\centering
	\caption{Configurations of Simian and NiCad}
	\label{t:param_tuning}
	\resizebox{\columnwidth}{!}{%
		\scriptsize
\begin{tabular}{l|p{5.5cm}}
	\hline 
	Tool & Parameters \\
	\hline
	Simian$_{\textrm{\textit{df}}}$ &  threshold=6, ignoreStringCase, \newline ignoreCharacterCase, ignoreModifiers \\ 
	\hline
	$S_E$ & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, ignoreStrings, \newline ignoreCharacters, ignoreSubtypeNames, \newline balanceSquareBrackets  \\ 
	\hline 
	$N_D$ & MinLine=10, MaxLine=1000, UPI=0.30 \\
	\hline
	$N_E$ & MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
	\hline 
\end{tabular} %
}
\end{table}

@@

\begin{table*}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering. The last column shows the number of true positive clone pairs after the manual investigation.}
	\label{tab:online_clone_pairs}
	\small
	\begin{tabular}{l|r|l|r|r|r|r}
		\hline
		Clone set & Original & Filter & Candidates & \texttt{equals()} & Manual & TP \\ 
		\hline 
		\multirow{1}{*}{\textit{good}} & --  & -- & 2,261  & 9 & 2,252 & 8 \\
		\multirow{1}{*}{\textit{ok}} & --  & -- & 26,838 & 9,122 & 200 & 47 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}        & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & $Line \geq 10$, RegEx, good/ok & 17,801 & 16,930 & 871 & 432 \\
		\multirow{1}{*}{$N_D$} & 229,176 & $Sim \geq 80\%$, RegEx, good/ok & 168 & 41 & 127 & 36 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 296,746 & & 47,068 & 26,102 & 3,450 & 523 \\ 
		\hline
	\end{tabular} 
\end{table*}

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}. The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. We found that NiCad generates errors and stopped processing against some Qualitas projects. \FIXME{Reported the errors to NiCad creator. Add response here.}  $N_D$ could not detect clones in 6 projects due to clustering errors. $N_E$ generated renaming and clustering errors for 11 and 16 projects respectively. As a result, we did not have NiCad clones from these project in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

\begin{table}
	\centering
	\caption{No.~of successfully analysed Qualitas projects}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		Execution & $S_D$ & $S_E$  & $N_D$ & $N_E$ \\ 
		\hline
		\textit{Successful} & 111 & 111 & 105 & 84 \\ 
		\textit{Clustering fail} & -- & -- & 6 & 16 \\
		\textit{Renaming fail} & -- &  -- & -- & 11 \\
		\hline
	\end{tabular}
\end{table}

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage[utf8]{inputenc}
\usepackage[italian]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{tikz}

@@

\begin{table}
	\centering
	\caption{Configurations of Simian and NiCad}
	\label{t:param_tuning}
%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|p{5.5cm}}
		\hline 
		Tool & Parameters \\
		\hline
		$S_D$ &  threshold=6, ignoreStringCase, \newline ignoreCharacterCase, ignoreModifiers \\ 
		\hline
		$S_E$ & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, ignoreStrings, \newline ignoreCharacters, ignoreSubtypeNames, \newline balanceSquareBrackets  \\ 
		\hline 
		$N_D$ & MinLine=10, MaxLine=1000, UPI=0.30 \\
		\hline
		$N_E$ & MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
		\hline 
	\end{tabular} %
%}
\end{table}

@@

\begin{table*}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering. The last column shows the number of true positive clone pairs after the manual investigation. }
	\label{tab:online_clone_pairs}
	\small
	\begin{tabular}{l|r|c|c|c|c|r|r|r|r}
		\hline
		\multirow{2}{*}{Clone set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Candidates} & \multirow{2}{*}{\texttt{equals()}} & \multirow{2}{*}{Manual} & \multirow{2}{*}{TP} \\ \cline{3-6}
		        		  & \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & & & & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & & & & & & 2,261  & 9 & 2,252 & 72 \\
		\multirow{1}{*}{\textit{ok}} &  & & & & & 9,322 & 9,122 & 200 & 9,240 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}        & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 & 16,930 & 871 & 704 \\
		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 168 & 41 & 127 & 116 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 296,746 & & & & & 47,068 & 26,102 & 3,450 & 10,132 \\ 
		\hline
	 	\multicolumn{10}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 80\%$, \textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}}
	\end{tabular} 
\end{table*}

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}. The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. We encountered NiCad failures with some Qualitas projects. \FIXME{Reported the errors to NiCad creator. Cordy said it might be a long-path problem. Should we try fixing?}  $N_D$ could not detect clones in 12 projects due to clustering errors. $N_E$ generated renaming and clustering errors for 11 and 17 projects respectively. As a result, we did not have NiCad clones from these project in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

\begin{table}
	\centering
	\caption{No.~of successfully analysed Qualitas projects}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		Execution & $S_D$ & $S_E$  & $N_D$ & $N_E$ \\ 
		\hline
		\textit{Successful} & 111 & 111 & 99 & 83 \\ 
		\textit{Clustering fail} & -- & -- & 12 & 17 \\
		\textit{Renaming fail} & -- &  -- & -- & 11 \\
		\hline
	\end{tabular}
\end{table}
